Pillar 1 - Sequential Pattern Mining

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd

#Mining-sequences:
The parameter values are: 
support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).
maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).

##Preparing data frame:
```{r}
fail_threshold <- 6.5

category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None

#this is new-----
transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
#----------------
d_sequence_transactions <- d_course %>%

  left_join(d_transcript, by = "Course ID") %>%
  # filter(!is.na(Grade)) %>% #remove NaN
  # filter(Grade != -1) %>% #remove NG
  mutate(
    Outcome = 
           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
                      Grade  > 5.5 ~"Pass",
                               T~"Fail"),
    Low_grade =
           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
                      Grade > fail_threshold ~"high score",
                               T~"low score"),
    Discrete_grade =
           case_when(Grade <= 5.4             ~ 5.0,
                     between(Grade, 5.5, 6.4) ~ 6.0,
                     between(Grade, 6.5, 7.4) ~ 7.0,
                     between(Grade, 7.5, 8.4) ~ 8.0,
                     between(Grade, 8.5, 9.4) ~ 9.0,
                     Grade >= 9.5             ~ 10.0,
                     T ~ -99999    #this is a control, we should not have any grades here
                     ),
    None= "" # this might not be optimal
         ) %>%

  mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade

  select(`Student ID`, Item, Time) %>%

  group_by(`Student ID`, Time) %>%

  summarize(list_course = list(Item)) %>%

  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))

##to transaction
```{r}
transaction_list_course <- d_sequence_transactions$list_course
names(transaction_list_course) <- d_sequence_transactions$TransactionID

transactions <- as(transaction_list_course, "transactions")
transactionInfo(transactions)$sequenceID <- d_sequence_transactions$`Student ID`
transactionInfo(transactions)$eventID <- d_sequence_transactions$Time
transactionInfo(transactions)$transactionID <- NULL

#checking results
as(transactions, "data.frame")
```

##Rule induction
##Creating look-up table
```{r}
lookup_table <- d_course %>%

>>>>

## CSPADE Algorithm

The parameter values are: 
support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).
maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).

##Creating look-up table
```{r}
lookup_table <- d_course %>%
